%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SPDX-License-Identifier: BSD-3-Clause
% Copyright (c) 2020, Salman Ahmad Faris
% https://github.com/salfaris/EasyPS
% Copyright (c) 2024, Daize Dong
% https://github.com/DaizeDong/Easier-PS-and-SoP
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass{easier_sop}

% --- ESSAY DISPLAY SETTINGS ---
\SetDocumentTitle{Personal Statement}
\SetStudentName{Leonardo Bove}           % Your name
\SetProgramName{PhD in Computer Science}           % Program you're applying for
\SetUniversityName{Northwestern University}     % University name
\SetUniversityAbbr{\GetUniversityName} % University abbreviation (default as the university name if not set)

% CONTENT
\begin{document}
	\thispagestyle{firstpageheader} % Use the expanded header on the first page
	
	Coming from a family where my parents’ highest degree is a high-school diploma, pursuing undergraduate and graduate studies—and now a PhD abroad—was not the expected path. They hoped I would enter the local workforce after high school, yet they consistently supported my curiosity for engineering and encouraged me to dream big while staying practical. This principle has guided my academic journey: advanced skills and knowledge should create tangible impact for individuals and society—for example, by helping make quantum-computing technologies accessible to all.
	
	During my studies in Pisa, I learned that meaningful achievements are possible only through collaboration. Serving as Chief Technology Officer of my university's Formula SAE team taught me what it means to be accountable for the success of one hundred people—and for our university’s reputation. We faced many challenges, but I learned to navigate them by coordinating individuals with diverse skills and supporting them both technically and empathetically: working alongside teammates during demanding tasks, sharing insights, and offering reassurance in stressful moments. This experience strengthened my technical abilities, confidence, and collaborative mindset.
	
	Achieving what once seemed impossible—building a competitive race car under tight time and budget constraints while fostering a cohesive team—played a pivotal role in my decision to pursue a graduate degree. I realized that I want to contribute to environments where people work together on impactful scientific questions, just as our team experience shaped each member’s growth. A research-focused degree is the natural continuation of that path and how I hope to create meaningful impact.
	
	
	\newpage
	\nocite{*} % show all the references
	%\bibliography{ref}
\end{document}