%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SPDX-License-Identifier: BSD-3-Clause
% Copyright (c) 2020, Salman Ahmad Faris
% https://github.com/salfaris/EasyPS
% Copyright (c) 2024, Daize Dong
% https://github.com/DaizeDong/Easier-PS-and-SoP
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass{easier_sop}

% --- ESSAY DISPLAY SETTINGS ---
\SetDocumentTitle{Personal Statement}
\SetStudentName{Leonardo Bove}           % Your name
\SetProgramName{PhD in Computer Science}           % Program you're applying for
\SetUniversityName{Northwestern University}     % University name
\SetUniversityAbbr{\GetUniversityName} % University abbreviation (default as the university name if not set)

% CONTENT
\begin{document}
	\thispagestyle{firstpageheader} % Use the expanded header on the first page
	
	Coming from a family where my parents’ highest degree is a high-school diploma, pursuing undergraduate and graduate studies—and now a PhD abroad—was not the expected path. They hoped I would enter the local workforce after high school, yet they always supported my curiosity for engineering and encouraged me to dream big while staying practical. This value has guided my academic journey: advanced skills and knowledge should create tangible impact for both individuals and society—for example, helping make quantum computing technologies accessible to all.
	
	During my academic journey in Pisa, I had the opportunity to learn how these concrete achievements that I aim to are feasible only through collaboration. The experience as Chief Technology Officer of the Formula SAE team of the University of Pisa taught me what it meant to be liable for the success or failure of a group of one hundred people, which strictly correlates to their satisfaction or regret, besides the reputation of our very own University. Many were the challenges that we had to face, however, I learned how to coherently tackle them by orchestrating people with different skills and guiding them towards the solution, both technically and empathically: working side-by-side to my team members in arduous tasks, suggesting technical tips from my experience, and giving hope and reassurance in the most stressful moments. Eventually this experience greatly improved not only my technical skills, but also and most importantly my self-confidence and collaboration attitude.
	
	Reaching the apparently impossible goal of developing a competitive racing car against challenging time and budget constraints, while building a cohesive team of people who grew with me, had a relevant role in my decision to pursue this graduate degree. In fact, I understood that I would like to be part and to actively contribute to similar environments, where the objective is to answer impactful academic questions, in the same way as the feelings and the experience of the team had a positive impact on the lives of its people. And I believe that a research focused degree would provide me with exactly that experience.
	
	
	
	
	\newpage
	\nocite{*} % show all the references
	%\bibliography{ref}
\end{document}